% The acknowledgements section is optional. It can cover at most two pages.
\acknowledge{
I would like to express my sincere gratitude to my advisor, Jiabin Wu, for his support, guidance, and extraordinary effort throughout my dissertation. His invaluable expertise and insightful advice have been instrumental in shaping this research and pushing it to new heights. I am truly grateful for his mentorship and friendship.

I would also like to extend my heartfelt appreciation to my co-author, Anne van den Nouweland, for her thorough edits and valuable contributions. Her meticulous attention to detail and rigorous analysis have greatly enhanced the precision of my writing and the robustness of my proofs. I am grateful for her collaborative spirit and the opportunity to learn from her expertise.

Additionally, I would like to acknowledge Van Kolpin for his valuable comments and suggestions. His input has been instrumental in refining the ideas presented in this dissertation, and I am thankful for his constructive feedback.

Lastly, I would like to express my deepest appreciation to my family, friends, and dogs for their unwavering encouragement and understanding throughout this endeavor. Their love, patience, and belief in me have been the driving force behind my accomplishments.

Without the support and contributions of all these individuals, this dissertation would not have been possible. I am truly grateful for their kindness, encouragement, and commitment to my success.

}

